The Weakly Nonlinear Standard and Helical Magnetorotational Instabilities in a Taylor Couette Flow

### 2016-07-14 paper/widegap_mri_paper.tex
more intro. needs more citations.

@@

\begin{table}[ht]
\normalsize
\caption{Fiducial parameters for MRI runs} \label{table:parameters}
\centering
%\resizebox{\textwidth}{!}
{\begin{tabular}{rlrrrrrrr}
  \hline
 & $\xi$ & $Pm$ & $\beta$ & $\Omega_2/\Omega_1$ & $R_1/R_2$ \\ 
  \hline\hline
Standard MRI & 0 & 1E-3 & 25 & 0.18 & 0.33 \\ 
Helical MRI & 4 & 1E-6 & 1.7E-2 & 0.27 & 0.5\\ 
   \hline
\end{tabular}}
\end{table}

@@

\bibitem[{Stefani et al.(2006)}]{Stefani:2006iv}
Stefani, F, Gundrum, T, Gerbeth, G, RŸdiger, G, Schultz, M, Szklarski, J, Hollerbach, R, Phys Rev Lett, 2006, 97, 184502

>>>>

Because of the MRI's complexity, analytical treatments of the MRI use some combination of convenient approximations: ideal MHD, linearized equations, expedient boundary conditions, and simplified geometries. In particular, much of the analytical work on MRI saturation has focused on local approximations, often representing a section of a disk by solving the MHD equations in an isolated region subject to shear periodic boundary conditions (the ``shearing box"). While the MRI is a local instability,

@@

\begin{table}[ht]
\normalsize
\caption{Fiducial parameters for MRI runs} \label{table:parameters}
\centering
%\resizebox{\textwidth}{!}
{\begin{tabular}{rlrrrrrrr}
  \hline
 & $\xi$ & $Pm$ & $\beta$ & $\Omega_2/\Omega_1$ & $R_1/R_2$ & radial magnetic b.c. \\ 
  \hline\hline
Standard MRI & 0 & 1E-3 & 25 & 0.18 & 0.33 & conducting \\ 
Helical MRI & 4 & 1E-6 & 1.7E-2 & 0.27 & 0.5 & insulating\\ 
   \hline
\end{tabular}}
\end{table}

@@

\bibitem[{Stefani et al.(2006)}]{Stefani:2006iv}
Stefani, F, Gundrum, T, Gerbeth, G, R\"udiger, G, Schultz, M, Szklarski, J, Hollerbach, R, Phys Rev Lett, 2006, 97, 184502
